Effects of Unemployment Benefits and Uncertainty in Heterogeneous Models

### 2017-01-23 presentation/presentation.tex
Change
Version3
Final version without references, include moments or not?
Added wealth consumption equiv graph

\begin{frame}{Life-time Utility}
  \begin{itemize}
  \item {
  We calculate the life-time utility of each agent when the economy is in steady state. One time before the policy change and once after the policy change.
  }
  \item {
  Cannot compare two steady states directly. We need to take the transition into account.
  }
  \item {
  Calculating the exact transition path is troublesome. We follow the approximation by Krussel, Mukoyama, and Sahin (2010) which takes care of the idiosyncratic transition.
  }
  	\begin{itemize}
  	\item {
  	Just place the agents in the first economy with their current assets into the second economy.
  	}
  	\end{itemize}
  \end{itemize}
\end{frame}

@@

\begin{frame}{Consumption Equivalent}
  \begin{itemize}
  \item {
  There exists a welfare increase in the mean and in the median.
  }
  \item {
  However, there is disagreement on whether to increase or decrease the unemployment benefits.
  }
  \item {
  Careful: the consumption equivalent is biased towards poorer agents as relative increases for them are higher than for already high-consumption agents.
  }
  \end{itemize}
\end{frame}

@@

\begin{frame}{Cash Equivalent}
  \begin{itemize}
  \item {
  There does not exist a higher welfare state in the mean, only in the median.
  }
  \item {
  If a higher welfare state existed for the mean we could redistribute wealth such that everyone would be better off. \\
  $\rightarrow$ Pareto improvement.
  }
  \item {
  One can clearly see the friction between unemployed and employed.
  }
  \end{itemize}
\end{frame}

@@

\begin{frame}{Cash vs. Consumption Equivalent}
  \begin{itemize}
  \item {
  Agents do not want full unemployment insurance although there is no moral hazard.
  }
  \item {
  Different groups in society want different policies. We did not find a policy reform that could make everyone better off.
  }
  \item {
  3
  }
  \end{itemize}
\end{frame}

>>>>

\begin{frame}{Life-time Utility}
  \begin{itemize}
  \item {
  We calculate the life-time utility of each agent when the economy is in steady state. One time before the policy change and once after the policy change.
  }
  \item {
  Cannot compare two steady states directly. We need to take the transition into account.
  }
  \item {
  Calculating the exact transition path is troublesome. We follow the approximation by Krussel, Mukoyama, and Sahin (2010) which takes care of the idiosyncratic transition.
  }
  	\begin{enumerate}
  	\item {
  	Just place the agents in the first economy with their current assets into the second economy.
  	}
  	\end{enumerate}
  \end{itemize}
\end{frame}

@@

\begin{frame}{Consumption Equivalent vs Wealth}
  \centering{\includegraphics[scale=0.6]{cons_equiv_wealth}}
\end{frame}

\begin{frame}{Consumption Equivalent}
\framesubtitle{Summary}
  \begin{itemize}
  \item {
  There exists a welfare increase in the mean and in the median.
  }
  \item {
  However, there is disagreement on whether to increase or decrease the unemployment benefits.
  }
  \item {
  Careful: the consumption equivalent is biased towards poorer agents as relative increases for them are higher than for already high-consumption agents.
  }
  \end{itemize}
\end{frame}

@@

\begin{frame}{Cash Equivalent}
\framesubtitle{Summary}
  \begin{itemize}
  \item {
  There does not exist a higher welfare state in the mean, only in the median.
  }
  \item {
  If a higher welfare state existed for the mean we could redistribute wealth such that everyone would be better off. \\
  $\rightarrow$ Pareto improvement.
  }
  \item {
  One can clearly see the friction between unemployed and employed.
  }
  \end{itemize}
\end{frame}

@@

\begin{frame}{Summary}
  \begin{itemize}
  \item {
  Agents do not want full unemployment insurance although there is no moral hazard.
  }
  \item {
  Different groups in society want different policies. We did not find a policy reform that could make everyone better off with certainty.
  }
  \item {
  Of course, the model is not complete. A next step would be to endogenize the unemployment rate such that it reacts to changes in unemployment benefits.
  }
  \end{itemize}
\end{frame}
